Responses to reviewers' comments and list of modifications done\\ on paper SORO226\\ \LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}

### 2011-07-17 cover_letter.tex
Raquel: polishing the rebuttal letter

@@

Below follow our answers to the reviewersÕ comments and suggestions. Each answer also indicates the changes made in the paper to address the reviewerÕs concern. An important number of language corrections are made, and the paper is proof-read by a native English speaker.

@@

We are aware that perception is not robust and therefore one of our next steps
is to include a probabilistic layer to the approach (as already mentioned in
the discussion section). We believe though that a robot (specially interacting
with people) should be allowed to make mistakes due to perception noise, or not
to be sure about something (for instance, "I think that..."), which represents
the uncertainty the robot has about a fact. In the meantime, to overcome
perception errors, the robot provides visual feedback (looking at objects) to
the user when possible and/or verifies the information with the user whenever
is needed (for instance, "do you mean the box\_01"?).

@@

Due to the perception problems and computational delays, fully realistic
settings are not yet possible.  The interaction based only on a static setting,
i.e. objects don't move, the interaction with a real user is accurate enough.
We have developed some experiments, where the user interacts with the system
only through a keyboard (no gestures are included) asking questions, providing
information, etc. and the outcome is quite promising. However, for dynamic
settings where the user can point at things, move the objects around, etc., the
interaction is not fast enough and the user should perform slow movements for
the robot to create a consistent state of world.

@@

Reviewer comment: ``The paper starts off with a discussion
of Austins speech act theory, including locutionary act, illocutionary force
and perlocutionary act. As the concept of speech acts is not really picked up
in the remainder of the paper, I do not see the point in starting with such a
discussion. It would be more appropriate to motivate how a robot could benefit
from a symbolic knowledge base etc.''

Austin's \emph{speech acts} were actually one of the starting point of our
analysis of dialogue understanding, and we think it is worthwhile to briefly mention
them in the introduction, as one of the theoritical ground of our work.

The reviewer however rightfully notes that \emph{perlocutionnary acts}, while mentioned, are not
actually used further. We moved this paragraph to a simple footnote.

@@

\begin{itemize}
\item All reviewer comments regarding citations have been addressed, following reviewer's suggestions,
\item The reviewer's remark on human tendency to explain in a consistent way the world has been added
\item Language issues have been addressed as well.
\end{itemize}

@@

The Open World assumption mainly allows us to model that we may not know
if a fact is true or not.

One very common example is the {\tt knowsAbout} predicate. This predicate
defines if some agent knows about some object.

It is important (especially for dialog) to be able to equally model that an agent knows or 
does not know about the object, or that the robot simply does not know if 
the human knows about it.

The Open World Assumption has important consequences on the reasoning
abilities of the system, since it prevents the classical "negation by 
failure" and leads to tighter modelling requirement to locally "close the
world" (for instance, the {\tt Color} class is defined as the equivalent of
the union of the 10 or so color instances we consider).

@@

The paragraph 2.2 has been reorganized to clarify the vocabulary and better
define the various acronyms.

@@

A mention to the Dora robot has been added in section 2.1.

@@

Numerous predicates in {\tt commonsense.oro.owl} are defined in the 
OpenCyc namespace: {\tt farFrom, near, hold-Underspecified, objectFoundInLocation}.

Similarly, most of the upper classes in the ontology belong to OpenCyc 
(like {\tt SpatialThing, PartiallyTangible, TemporalThing}...).

Overall, about 50 entites (on the >180 defined in {\tt commonsense.oro.owl}) 
come from OpenCyc.

Since most of the upper classes are OpenCyc concepts, this should 
guarantee to a certain extend the alignment of our ontology with other ontologies.

@@

\subsection{``p.6, II.E. Explain "multi-lingual support"''}

The "multi-lingual support" has been reworded:

``fast concept lookup, with possible multi-lingual support (through the
{\tt @lang} XML annotation, labels of concept can be translated, and
specific translations can be queried for)''

@@

PointsAt relation is computed continuously during the interaction by 
selecting the objects that "might" be pointed at by the human. The outcome
of the computation (facts like "human1 pointsAt bottle1") are then
continously updated in the knowledge base.

In the current system, the decision on whether the human is pointing at an 
object in a given time is left to the reasoning on the dialog or on the human gestures:
when the dialogue module analyses a sentence like "give me this", it tries to
resolve the atom "this" by querying the ontology.

Both sitatuation assessement and dialogue processing chains induce 
small delays, but these are roughly the same (below 200ms), and 
compensate for each other.

@@

Kelleher's work, as well as Blisard's, are now correctly cited in the section.

@@

We thank the reviewer for this input that has been added to the article.

\subsection{``p.9, Alg. IV.1: the crucial bits are left out; please explain
"GenerateDescription", "Ontology.Find", "Ontology.CheckEquivalent", and
"Discrimination"''}

@@

The detailled algorithm is provided in appendix to this letter.
We would be happy to add it to the paper as well if the editor want to consider it.

>>>>

\newcommand{\stmt}[1]{{\footnotesize $\langle$\stmttt#1\relax$\rangle$}}

@@

We next answer the reviewers comments and suggestions. Besides, each answer
indicates the changes made in the paper to address the reviewers' concerns. An
important number of language corrections have been made, and the paper has been
proof-read by a native English speaker.

@@

We are aware that perception is not robust and therefore one of our next steps
is to include a probabilistic layer to the approach (as already mentioned in
the discussion section). We believe though that a robot (specially interacting
with people) should be allowed to make mistakes due to perception noise, or not
to be sure about something (for instance, ``I think that..."), which represents
the uncertainty the robot has about a fact. In the meantime, to overcome
perception errors, the robot provides visual feedback (looking at objects,
showing in screen its 3D model of the environment) to the user when possible
and/or verifies the information with the user whenever is needed (for instance,
``do you mean the box\_01"?).

@@

Due to perception problems and computational delays, fully realistic settings
are not yet possible. In static settings, where neither humans nor objects
move, the interaction with real users is meaningful and the flow of information
between robot and user is accurate enough.  We have developed some experiments
where the user interacts with the system only through a keyboard (no gestures
are included) asking questions, providing information, etc. and the outcome is
quite promising. However, for dynamic settings, where the user can point at
things, move the objects around, etc., the interaction is not fast enough and
the user should perform slow movements for the robot to create a consistent
state of world.

@@

%Reviewer comment: ``The paper starts off with a discussion
%of Austins speech act theory, including locutionary act, illocutionary force
%and perlocutionary act. As the concept of speech acts is not really picked up
%in the remainder of the paper, I do not see the point in starting with such a
%discussion. It would be more appropriate to motivate how a robot could benefit
%from a symbolic knowledge base etc.''

The analysis of dialogue understanding we have followed has been inspired by
Austin's \emph{speech acts}. Thus, we believe it is worthwhile to briefly mention
them in the introduction as a theoretical ground of our work.

However, since we do not directly refer to them in the remainder of the paper,
we refer to Austin's definitions in a footnote.

@@

\begin{itemize}
\item All reviewer's comments regarding citations have been addressed.
\item The reviewer's remark on human tendency to explain in a consistent way the world has been added.
\item Language issues have been addressed as well.
\end{itemize}

@@

The Open World assumption mainly allows us to model that we may not know if a
fact is true or not. A common example is the {\tt knowsAbout} predicate. This
predicate defines if some agent knows about some object. It is important
(especially for dialog) to model that an agent knows or  does not know about an
object, or that the robot simply does not know if the human knows about it.

The Open World Assumption has important consequences on the reasoning
abilities of the system, since it prevents the classical ``negation by 
failure" and leads to tighter modelling requirement to locally ``close the
world" (for instance, the {\tt Color} class is defined as the equivalent of
the union of the 10 or so color instances we consider).

@@

Paragraph 2.2 has been reorganized to clarify the vocabulary and better
define the various acronyms.

@@

A reference to the Dora robot has been added in section 2.1. However, at the
time when this work had been submitted for review, neither of the two proposed
papers by the reviewer were available (and in fact, IJCAI is taking place this
week).

@@

Numerous predicates in {\tt commonsense.oro.owl} are defined in the OpenCyc
namespace: {\tt farFrom, near, hold-Underspecified, objectFoundInLocation} are
some of examples. Similarly, most of the upper classes in our ontology belong
to OpenCyc (e.g. {\tt SpatialThing, PartiallyTangible, TemporalThing},...).
Overall, about 50 entities (from the more than 180 defined in {\tt
commonsense.oro.owl}) come from OpenCyc.

Since most of the upper classes are OpenCyc concepts, this should 
guarantee, to a certain extend, the alignment of our ontology with other ontologies.

@@

\subsection{``p.6, II.E. Explain ``multi-lingual support"''}

The ``multi-lingual support" part has been reworded (Section 2.5.1).

@@

SPARK is continuously updating the human non-verbal queues included in this
work (i.e., looking at, pointing at, etc.). The outcome of these computation
(facts like {\tt $\langle$human1 pointsAt bottle\_01$\rangle$}) are then
constantly been sent to the knowledge base.

In the current approach, the timing aspect is managed during the analysis of
dialogue. When the user makes reference to an object through demonstratives
(e.g. this, that), the DIALOGS module queries the ontology for objects being
pointed at. The assumption for this mechanism to work is that the human is
constantly pointing while the dialog analysis takes place.  Both situation
assessment and dialogue processing chains induce small delays, but these are
roughly the same (below 200ms), and compensate for each other.

Section 3.1. and 5.3.3. clarify this point.

@@

Kelleher's work, as well as Blisard's, are now cited in the section.

@@

We thank the reviewer for this input, which has been added to the article.

\subsection{``p.9, Alg. IV.1: the crucial bits are left out; please explain
``GenerateDescription", ``Ontology.Find", ``Ontology.CheckEquivalent", and
``Discrimination"''}

@@

The detailled algorithm is provided in appendix to this letter.  We would be
happy to add it to the paper as well if the editor wants to consider it.
